A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-24 manuscript.Rmd
explain what is still missing
close #3

We deem each concept necessary to archive longterm reproducibility.
However, which tools you use to implement these concepts is a matter of taste and project requirements.
This tutorial follows the recommendations of @Peikert2019 and utilize Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking, and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.

@@

Recording each change you made helps you to iterate more quickly because you know that you can effortlessly go back to previous versions.
For example, you can write down a rough project idea, knowing your collaborators and you will iterate and improve.
<!-- This is maybe the place to introduce the example-->
First, you could create a new markdown file named `idea.md` that looks like this:

@@

<!--Hands on: Introduce RMarkdown-->
<!--Hands on: gitignore resulting .html/pdf-->
<!-- A preregistration needs to be public -->

@@

>>>>

We deem each concept necessary to archive longterm reproducibility.
However, which tools you use to implement these concepts is a matter of taste and project requirements.
This tutorial follows the recommendations of @Peikert2019 and utilize Git for version control, R Markdown for dynamic document creation, Make for dependency tracking, and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.

@@

Recording each change you made helps you to iterate more quickly because you know that you can effortlessly go back to previous versions.
For example, you can write down a rough project idea, knowing your collaborators and you will iterate and improve.
<!-- This is maybe the place to introduce the example-->
First, you could create a new Markdown file named `idea.md` that looks like this:

@@

<!--Hands on: Introduce R Markdown-->
<!--Hands on: gitignore resulting .html/pdf-->
<!-- A preregistration needs to be public -->

@@

While you already know how to write dynamic documents with [Markdown] and [R Markdown], and track changes with [Git] and [GitHub], two components to archive longterm reproducibility are still missing.
